Fig2: Candidate genes

### 2020-04-18 analysis/figure-1.Rmd
now with full table

```{r}
suppletable1 <- allDEG %>%
  filter(comparison != "control_bldg") %>%
  group_by(sex, tissue, comparison) %>%
  arrange( tissue, sex, direction, gene)
head(suppletable1)

>>>>

```{r}
suppletable1 <- allDEG %>%
  #filter(comparison != "control_bldg") %>%
  group_by(sex, tissue, comparison) %>%
  arrange( tissue, sex, direction, gene)
head(suppletable1)

### 2020-04-18 analysis/figure-2.Rmd
now with full table

table1 <- left_join(candidateDEGS, GOgenesWide) %>%
  select(gene, bldg_lay:n5_n9, parentalcare, parentalbehavior, NCBI) %>%
  mutate(parentalcare = if_else(is.na(parentalcare), " ", "X"),
         parentalbehavior = if_else(is.na(parentalbehavior), " ", "X")) %>%
  rename("Literature" = "parentalcare", "GO" =  "parentalbehavior")
table1[is.na(table1)] <- " "
table1

>>>>

table1 <- left_join(candidateDEGS, GOgenesWide) %>%
  select(gene, bldg_lay:n5_n9, parentalcare, parentalbehavior, NCBI) %>%
  mutate(parentalcare = if_else(is.na(parentalcare), " ", "X"),
         parentalbehavior = if_else(is.na(parentalbehavior), " ", "X")) %>%
  rename("Literature" = "parentalcare", "GO" =  "parentalbehavior")
table1$numDEGs <- rowSums(is.na(table1)) # count NAs to know how many are NS
table1 <- table1 %>% 
  mutate(sig = ifelse(numDEGs == 6, "NS", "DEG")) %>% 
  arrange(sig, gene)  %>%  select(-sig, -numDEGs)
table1[is.na(table1)] <- " " # replace NA with blank space so it's pretty
#table1
